Optimal (Multiway) Spatial Joins

### 2024-06-01 5.1.tex
5.1

We argue that $\bm{t}\in \J_2$. Let $p$ be the intersection of $h'$ and $v$. Since $(r_1,...,r_{k-3}, h', v) \in \J(R_1,...,R_{k-3},H',V)$, $p \in r_i$ for $i \in [k-3]$. As we proved in the last paragraph, $r_{k-2}$ covers $h'$, so $p \in r_{k-2}$. Additionally, $r_{k-2}$ covers the left endpoint of $h$. Therefore, $\bm{t} \in \J_2$.

>>>>

We argue that $\bm{t}\in \J_2$. Let $p$ be the intersection point of $h'$ and $v$. As $h' \subseteq h$, the intersection point of $h$ and $v$ is also $p$.
Since $(r_1,...,r_{k-3}, h', v) \in \J(R_1,...,R_{k-3},H',V)$, $p \in r_i$ for $i \in [k-3]$. As shown in the last paragraph, $r_{k-2}$ covers $h'$, so $p \in r_{k-2}$. Thus, $h \cap v \bigcap_{i = 1}^{k-2}r_i \neq \emptyset$, and $\bm{t} \in \J(R_1,...,R_{k-2},H,V)$.
 Additionally, $r_{k-2}$ covers the left endpoint of $h$. Therefore, $\bm{t} \in \J_2$.
